Allocation scores, WIS, and CRPS via decision theory

### 2023-08-20 alloscore_manuscript/methods_apg.tex
add z to ias/crps

\begin{align}
s_{t\mathrm{WIS}}(x^{F,t\mathrm{WIS}},y) &= \frac{1}{m}\sum_{l=1}^N \sum_{i=1}^{m}s_{Q}(x_{l,i}^{F_l,\mathrm{Q}, C_i}, y_l)_+ \\ 
&= \frac{1}{m} \sum_{i=1}^{m}s_{\mathrm{AS}}(x^{F,\mathrm{AS},  K(C_i, F, L)},y) 
\end{align}

\begin{align}
s_{\mathrm{IAS}}(x^{F, \mathrm{IAS}}(k), y) &= \int_0^{\infty} s_{\mathrm{AS}}(x^{F, \mathrm{AS}(k)}, y) dk \\
&= \int_0^{\infty} \sum_{l=1}^N s_{\mathrm{Q}}(x^{F_l, \mathrm{Q}(c(k, F))}, y) dk \\
&= \sum_{l=1}^N \int_0^{\infty} s_{\mathrm{Q}}(x^{F_l, \mathrm{Q}(c(k, F))}, y) dk
\end{align}

>>>>

\begin{align}
s_{t\mathrm{WIS}}(x^{F,t\mathrm{WIS}},y) &= \frac{1}{m}\sum_{l=1}^N \sum_{i=1}^{m}(x_{l,i}^{F_l,\mathrm{Q}, C_i}- y_l)_+  + C_i x_{l,i}^{F_l,\mathrm{Q}, C_i}\\ 
&= \frac{1}{m} \sum_{i=1}^{m}s_{\mathrm{AS}}(x^{F,\mathrm{AS},  K(C_i, F, L)},y) + C_i K(C_i, F, L)
\end{align}

\begin{align}
s_{\mathrm{IAS}}(x^{F, \mathrm{IAS}}(k), y) &= \int_0^{\infty} s_{\mathrm{AS}}(x^{F, \mathrm{AS}(k)}, y) dk \\
&= \int_0^{\infty} \sum_{l=1}^N s_{\mathrm{Q}}(x^{F_l, \mathrm{Q}(c(k, F))}, y) - c(k, F)kdk \\
&= \sum_{l=1}^N \int_0^{\infty} s_{\mathrm{Q}}(x^{F_l, \mathrm{Q}(c(k, F))}, y) dk -  \int_0^{\infty} c(k, F)kdk
\end{align}
